Value Ordering, Discrepancies, and Restarts for Subgraph Isomorphism

### 2017-12-13 paper/paper.tex
Edity

The performance of the two degree heuristics are very similar: the
biased heuristic has slightly worse performance below a 100s timeout, and effectively equal
performance above it. This shows that we can introduce an element of randomness into the degree
value-ordering heuristic without adversely affecting its performance \emph{in aggregate}.
\Cref{figure:scatter-heuristics} gives a more detailed look at these results. In this plot,
satisfiable and unsatisfiable instances are shown using coloured shapes and black dots respectively.
On the $x$-axis we measure the degree heuristic, whilst on the $y$-axis we measure the biased
heuristic. Points on the outer axes represent instances which timed out with one heuristic but not
the other.  This plot shows that despite the aggregate performance being very similar, on an case by
case basis, the two heuristics can make a large difference to the performance of satisfiable
instances.

@@

\Cref{figure:restarts} shows that either biased heuristic together with restarts is better
still---that is, if we are introducing restarts, then it is better to add a small amount of
randomness to a tailored deterministic heuristic than it is to throw away the heuristic altogether.
The degree-biased heuristic is also stronger than position-biased, showing that exploiting ties and
relative sizes in the heuristic ordering is also worthwhile. Interestingly, the gap between degree-
and position-based is much larger when using restarts than it is when not using them.

@@

\begin{itemize}
    \item The choice of Luby multiplier is not hugely important, although 100 is too small and 1,000
        is too big.
    \item The base of the exponential does not have to be $e$, and it may be easier on implementers
        to use 2. Using a polynomial weighting is bad, and using a base of $|D_v|$ is bad.
    \item Using geometric restarts instead of Luby does not give much of a benefit. A constant
        restart policy is also fine (and terminates on unsatisfiable instances because we count
        backtracks).
    \item Using rank with restarts is better than random with restarts, but not as good as using
        biased with restarts.
    \item Nogood recording is important.
    \item Nogood recording is cheap.
    \item Discarding subsumed nogoods may be done cheaply, if memory space is a concern.
\end{itemize}

>>>>

The performance of the two degree heuristics are very similar: the
biased heuristic has slightly worse performance below a 400s timeout, and effectively equal
performance above it. This shows that we can introduce an element of randomness into the degree
value-ordering heuristic without adversely affecting its performance \emph{in aggregate}.
\Cref{figure:scatter-heuristics} gives a more detailed look at these results. In this plot,
satisfiable and unsatisfiable instances are shown using coloured shapes and black dots respectively.
On the $x$-axis we measure the degree heuristic, whilst on the $y$-axis we measure the biased
heuristic. Points on the outer axes represent instances which timed out with one heuristic but not
the other.  This plot shows that despite the aggregate performance being very similar, on an case by
case basis, the two heuristics can make a large difference to the performance of satisfiable
instances.

@@

\Cref{figure:restarts} shows that either biased heuristic together with restarts is better
still---that is, if we are introducing restarts, then it is better to add a small amount of
randomness to a tailored deterministic heuristic than it is to throw away the heuristic altogether.

@@

\begin{itemize}
    \item The choice of Luby multiplier is not hugely important, although 100 is too small and 1,000
        is too big.
    \item The base of the exponential can be $2$ or $e$ or $3$ or $1.5$ and it makes little
        difference. Using a polynomial weighting is bad, and using a base of $|D_v|$ is bad.
    \item Using geometric restarts instead of Luby does not give as much of a benefit. A constant
        restart policy is also fine (and terminates on unsatisfiable instances because we count
        backtracks).
    \item Using rank with restarts is better than random with restarts, but not as good as using
        biased with restarts.
    \item Nogood recording is important.
    \item Nogood recording is cheap.
    \item Discarding subsumed nogoods may be done cheaply, if memory space is a concern.
\end{itemize}
